### 2023-08-28 about/vita.tex
Density increment and misc things

\leftright{Citizen of Canada and Singapore}{2-9602 74th Avenue NW}
\leftright{Email: marcel\_goh@yahoo.ca}{Edmonton, AB T6E 1E6}
\leftright{Webpage: marcelgoh.ca}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4.
Thesis: Structural properties of conditional Galton--Watson trees.
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf NSERC Canada Graduate Scholarship -- Master's \rm (\$17,500)}{\bf May 2021 -- April 2022}
\smallskip
\leftright{\bf NSERC Undergraduate Student Research Award \rm (\$7,125)}{\bf May -- August 2020}
\smallskip
\leftright{\bf Governor General's Academic Medal -- Bronze}{\bf June 2015}

\sectheader{Graduate-level Coursework}

Higher algebra (categories, groups, modules), functional analysis, quadratic and modular forms, combinatorics,
topology (including some algebraic topology), probabilistic analysis of algorithms.

@@

Analysis of random discrete structures, analysis and design of algorithms, enumerative combinatorics,
additive combinatorics.

@@

@@

\starleftright{\bf Teaching assistant}{\bf September -- December 2021}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Held office hours twice a week and responsible for grading of assignments.
\medbreak

>>>>

\leftright{Citizen of Canada and Singapore}{5872 Esplanade Avenue}
\leftright{Email: marcel\_goh@yahoo.ca}{Montreal, QC H2T 3A3}
\leftright{Webpage: marcelgoh.ca}{+1\thinspace\up(825\up)\thinspace 440-0681}

@@

\leftright{\bf Ph.D.\ Mathematics}{\bf September 2023 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisors: Andrew Granville and Hamed Hatami.
\medbreak
\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4.
Thesis: Structural properties of conditional Galton--Watson trees.
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

\leftright{\bf NSERC Canada Graduate Scholarship -- Doctoral
\rm (\$105,000)}{\bf September 2023 -- August 2026}
\smallskip
\leftright{\bf FRQNT Bourse de doctorat en recherche
\rm (\$100,000)}{\bf [Declined]}
\smallskip
\leftright{\bf NSERC Canada Graduate Scholarship -- Master's \rm (\$17,500)}{\bf May 2021 -- April 2022}
\smallskip
\leftright{\bf NSERC Undergraduate Student Research Award \rm (\$7,125)}{\bf May -- August 2020}
\smallskip
\leftright{\bf Governor General's Academic Medal -- Bronze}{\bf June 2015}

@@

Additive combinatorics, analytic number theory, random trees, analysis of algorithms.

@@

\starleftright{\bf Teaching assistant}{\bf September 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant in the following courses. Duties include giving tutorials, holding office hours, and
grading assignments and exams.
\begingroup\parindent=10pt
\smallskip
\thing Fall 2023: MATH 240 Discrete Structures
\smallskip
\thing Fall 2021: COMP 690 Probabilistic Analysis of Algorithms
\endgroup
\medbreak

@@
